\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{mathrsfs}
\usepackage{comment}
%\newtheorem{definition}{Definition}
%\usepackage{algorithmicx}
%\usepackage{algorithm} % http://ctan.org/pkg/algorithms

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{2017}
\copyrightyear{2017}

%\acmPrice{15.00}


\begin{document}
\title{Temporal Motif Mining Approaches for Smart Homes}
%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{
  Huijuan Shao\textsuperscript{1,2}, Yaowei Li\textsuperscript{3}, Fei Li\textsuperscript{2}, Erin Griffiths \textsuperscript{4}, Kamin Whitehouse\textsuperscript{4}, Naren Ramakrishnan\textsuperscript{1,2} \\
  \textsuperscript{1}Discovery Analytics Center, Virginia Tech, Blacksburg, VA 24061 \\ %\vspace{0.1cm}
  \textsuperscript{2}Department of Computer Science, Virginia Tech, Blacksburg, VA 24061 \\ %\vspace{0.1cm}
    \textsuperscript{3} Game source, McLean, VA 22101 \\
  \textsuperscript{4}Department of Computer Science, University of Virginia, VA 22904 \\ %\vspace{0.1cm}
}




% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
With the advent of modern sensor technologies, 
significant opportunities have opened up to help conserve energy in 
residential and commercial buildings. Moreover, the rapid \emph{urbanization} we are witnessing requires optimized energy distribution. 
This paper focuses on two sub-problems in improving energy conservation; \emph{energy disaggregation and occupancy prediction}. 
Energy disaggregation attempts to 
separate the energy usage 
of each circuit or each electric device in a building 
using only aggregate electricity usage information from 
the meter for the whole house. 
The second problem of occupancy prediction can be accomplished using non-invasive indoor activity tracking to 
predict the locations of people inside a building. 
We cast both problems as \emph{temporal mining problems}. We exploit motif mining with constraints to distinguish devices with multiple states, which helps tackle the energy disaggregation problem. Our
results reveal that motif mining is adept at distinguishing
devices with multiple power levels and at disentangling the
combinatorial operation of devices.
For the second problem we propose time-gap constrained episode mining to detect 
activity patterns followed by the use of a mixture of episode generating HMM (EGH) models 
to predict home occupancy.  
Finally, we demonstrate that the mixture EGH
model can also help predict the location of a person to 
address non-invasive indoor activities tracking. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%


\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\include{sec/introduction}
\include{sec/prior}
%\include{sec/multivariateApp}
\include{sec/predictionApp}
%\include{sec/disaggResults}
\include{sec/predictionResults}
\input{sec/conclusion.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references} 

\end{document}
